High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 PandaOverview.tex
A bit more space saving

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 2: use of wrong wordings, such as "eventful" instead of
	the common term "stateful".\mtnote{Done.}
\end{itemize}
\fi

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \vspace{-0.3in}
    \caption{PanDA WMS architecture. Numbers indicates the JEDI-based
    execution process described in \S\ref{sec:panda_overview}. Several
    subsystems, components, and architectural and communication details are
    abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

>>>>

% \ifreview
% Comments to address in this section:
% \begin{itemize}
% 	\color{red} 
% 	\item REVIEWER 2: use of wrong wordings, such as "eventful" instead of
% 	the common term "stateful".\mtnote{Done.}
% \end{itemize}
% \fi

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \vspace{-0.3in}
    \caption{PanDA WMS architecture. Numbers indicates the JEDI-based
    execution process described in \S\ref{sec:panda_overview}. Several
    subsystems, components, and architectural and communication details are
    abstracted to improve clarity.}\label{fig:architecture}
\end{figure}
